Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?

### 2024-09-08 submission/responseletter.tex

\theoremstyle{definition}
\newtheorem{de}{Definition}
\newtheorem{lm}{Lemma}
\newtheorem{exm}{Example}
\theoremstyle{remark}
\newtheorem{Alg}{Algorithm}
\newtheorem{rem}{Remark}
\bibliographystyle{agsm}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}
%\doublespace
\let\code=\texttt
\begin{document}

\begin{center}
%\maketitle
\setlength{\unitlength}{2cm}

{\Large Responses to Associate Editor and Referee's Comments \\[%
0pt]
\vspace{0.02in}
\large\textbf{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}}
\end{center}

\noindent We greatly appreciate the time and effort the Associate Editor and the two referees have dedicated to reviewing our paper. We have provided a reproducibility package in \url{https://github.com/AngelPone/project_hierarchy}.

\newpage

@@

\section*{Comments from Referee 1}

\textit{I am satisfied with the revisions made by the authors in response to my comments. They have addressed all my suggestions thoroughly and clearly, improving the quality of the manuscript.}

\textbf{Response:} Thank you for your review and valuable comments.

\newpage

@@

\section*{Comments from Referee 2}

\textit{Thank you for the clarifications you have provided, I think they are very helpful. The paper is useful and insightful, well done!}

\textbf{Response:} Thank you for your review and valuable comments.

\end{document}

### 2024-09-08 submission/coverletter.tex
fix

Thank you for giving us the opportunity to revise and resubmit this paper. We hope that the incorporation of the suggested changes will now make the revised paper suitable for \textit{International Journal of Forecasting}. We have addressed the comments from the Associate Editor and the two reviewers in separate files.    \\

>>>>

Thank you for conditionally accepting our paper for publication in \textit{International Journal of Forecasting}. We have made a reproducibility package available in an online GitHub repository, which can be accessed at \url{https://github.com/AngelPone/project_hierarchy}.    \\
